```{r}
library(AppliedPredictiveModeling)
data(solubility)
library(lattice)
library(e1071)
library(caret)
library(corrplot)
library(ggbiplot)
```
Ploting Some Histograms of note binary data

```{r}
colors = colors()

hist(solTrainX$MolWeight, 
     main="MolWeight",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumAtoms, 
     main="NumAtoms",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumNonHAtoms, 
     main="NumNonHAtoms", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumBonds, 
     main="NumBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumNonHBonds, 
     main="NumNonHBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumMultBonds, 
     main="NumMultBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumRotBonds, 
     main="NumRotBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumDblBonds, 
     main="NumDblBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumAromaticBonds, 
     main="NumAromaticBonds",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumHydrogen, 
     main="NumHydrogen",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumCarbon, 
     main="NumCarbon",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumNitrogen, 
     main="NumNitrogen", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumOxygen, 
     main="NumOxygen", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumSulfer, 
     main="NumSulfer",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumChlorine, 
     main="NumChlorine", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumHalogen, 
     main="NumHalogen", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$NumRings, 
     main="NumRings", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$HydrophilicFactor, 
     main="HydrophilicFactor",
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$SurfaceArea1, 
     main="SurfaceArea1", 
     border="blue", 
     col=sample(colors, 1),
     las=1)

hist(solTrainX$SurfaceArea2, 
     main="SurfaceArea2", 
     border="blue", 
     col=sample(colors, 1),
     las=1)
```



Matrix mean, deviation and skewness
Generating a table with mean, deviation and skewness
Creating the matrix with 228 rows and 3 colums

```{r}
A = matrix(nrow=228, ncol=3)

mean_sd_skewness <- function(data) {
  
  dimnames(A) = list(
    colnames(data),
    c("mean", "deviaton", "skewness")
  )
  
  ncoluns = dim(data)[2]
  for(i in 1:ncoluns) {
    A[i, 1] = mean(data[,i])
    A[i, 2] = sd(data[,i])
    A[i, 3] = skewness(data[,i])
  }
  print(A)
}

```


initial plots

```{r}
xyplot(solTrainY ~ solTrainX$MolWeight, type = c("p","g"), ylab = "Solubility", xlab = "Mol Weight")
xyplot(solTrainY ~ solTrainX$SurfaceArea1, type = c("p","g"), ylab = "Solubility", xlab = "Surface Area 1")
bwplot(solTrainY ~ ifelse(solTrainX[,50] == 1, "presence", "absent"), ylab = "Solubility")
```


transformar apenas os FP

```{r}
#notfps = names(solTrainX)[!grepl("FP", names(solTrainX))]
train_X <- solTrainX[,209:228] + 1
test_X  <- solTestX[,209:228] + 1


```

pre process

```{r}
solPP <- preProcess(train_X, method = c("BoxCox", "center", "scale"))
predTrainX <- predict(solPP, train_X)
predTestX <- predict(solPP, test_X)
```


Junta os preditores e as variáveis transformadas

```{r}
solTrainTransX <- cbind(solTrainX[,grep("FP", names(solTrainX))],predTrainX)
solTestTransX <- cbind(solTestX[,grep("FP", names(solTestX))],predTestX)

```


```{r}

skewness(solTrainXtrans$MolWeight)
skewness(solTrainTransX$MolWeight)

#mean_sd_skewness(solTrainXtrans)
mean_sd_skewness(solTrainTransX)
```

Correlation Matrix

```{r}
correlation_matrix = cor(solTrainTransX[, 209:228])
corrplot(correlation_matrix, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

PCA Analises

```{r}
Glasspca = prcomp(solTestTransX[, 209:228])
summary(Glasspca)
ggbiplot(Glasspca, ellipse = TRUE)
```


regressão linear

```{r}

folds = createFolds(solTrainY, k = 5, returnTrain = TRUE)
ctrl_folds = trainControl(method = "cv", index = folds, number = 5)
lmTrain = train(x = solTrainTransX,y = solTrainY, method = "lm", trControl = ctrl_folds, preProcess = c("BoxCox"))

lmTrain

```



model tuning

```{r}
correlated1 = findCorrelation(cor(solTrainTransX), .9)
#correlated2 = findCorrelation(cor(solTestTransX), .9)
filteredTrainX <- solTrainTransX[,-correlated1]
#filteredTestX <- solTestTransX[,-correlated2]

q <- solTrainTransX[,209:228][,-findCorrelation(cor(solTrainTransX[,209:228]), .9)]
corrplot::corrplot(cor(q))

lmTrainTune <- train(x = filteredTrainX, y = solTrainY, method = "lm", trControl = ctrl_folds)

lmTrainTune
```


define rsquared

```{r}
rsq <- function (x, y) cor(x, y) ^ 2
```



```{r}
pred_ = predict(lmTrainTune,solTestXtrans)
head(pred_)
postResample(solTestY,pred_)
RMSE(solTestY,pred_)
lmTrainTune$resample
```



```{r}
resultados = data.frame(obs = solTestY, pred = pred_)
defaultSummary(resultados)
plot(solTestY ~ .,resultados)
residuals <- resid(lmTrain)
fits <- fitted(lmTrain)
plot(fits,residuals)

```

Penalized Models

```{r}
indx <- createFolds(solTrainY, returnTrain = TRUE)
ctrl <- trainControl(method = "cv", number = 10)
ridgeGrid <- data.frame (.lambda = seq(0, .1, length = 15))
set.seed(100)
ridgeRegFit <- train(solTrainXtrans,solTrainY,
method = "ridge",
tuneGrid = ridgeGrid,
trControl = ctrl,
preProc = c("center", "scale"))
ridgeRegFit
```


```{r}
print(update(plot(ridgeRegFit), xlab = "Penalty"))
```

```{r}
enetGrid <- expand.grid(lambda = c(0, 0.01, .1),
fraction = seq(.05, 1, length = 20))
set.seed(100)
enetTune <- train(x = solTrainXtrans, y = solTrainY,
method = "enet",
tuneGrid = enetGrid,
trControl = ctrl,
preProc = c("center", "scale"))
enetTune
plot(enetTune)
```



use the training transformed predictor to learn either PCR or PLS and test using test set

```{r}
custom_folds = createFolds(solTrainY, k = 10, returnTrain = TRUE)
custom_tcl = trainControl(method = "cv", index = custom_folds, number = 10)
pls_ = train(x = solTrainTransX, y = solTrainY, method = "pls", trControl = custom_tcl, preProcess =  c("BoxCox"), tuneLength = 5)

pls_

resultPls = predict(pls_,solTestXtrans)
frame_pls = data.frame(obs = solTestY, pred = resultPls)
defaultSummary(frame_pls)

#RMSE(solTestY,plsPred)
#postResample(solTrainXtrans,plsResults)


```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
